Capstone Movielens Report

### 2025-10-22 reports/capstone-movielens.site/05.appendix.Rmd
Functions describing: msg.set_arg, msg.glue (in progress)

>>>>

#### [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) Function {#func.msg.set_arg}
\

Builds a message string from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:
  - [arg.name](#func.msg.set_arg.args.arg.name): name of the element; 
  - [arg](#func.msg.set_arg.args.arg): the element value.

::: { #func.msg.set_arg.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
msg.set_arg(msg_template, arg, arg, arg.name = "%1")
```
:::

::: { #func.msg.set_arg.args .sidebar }
##### Arguments
\

::: { #func.msg.set_arg.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

::: { #func.msg.set_arg.args.arg.name .sidebar }
  - **arg.name:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument. 
:::

::: { #func.msg.set_arg.args.arg .sidebar }
  - **arg:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.msg.set_arg.args.msg_template) argument.

::: { #func.msg.set_arg.details .sidebar }
##### Details
\

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.msg.set_arg.args.msg_template) and [arg](#func.msg.set_arg.args.arg)  arguments, respectively.

::: { #func.msg.set_arg.value .sidebar }
##### Value
\

::: { #func.msg.set_arg.code .sidebar }
##### Source Code
\

The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) function is shown below:
```{r eval=FALSE}
msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
  msg_template |> 
    str_replace_all(arg.name, as.character(arg))
}
```

::: {.noteblock data-latex=""}
The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) function is defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) script on _GitHub_.
:::
:::

#### [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) Function {#func.msg.glue}
\

Builds a message string from the template passed in the [msg_template](#func.msg.glue.args.msg_template) argument using the format element specified by the following arguments:
  - [arg.name](#func.msg.glue.args.arg.name): name of the element; 
  - [arg](#func.msg.glue.args.arg): the element value.

::: { #func.msg.glue.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
msg.glue(msg_template, arg, arg, arg.name = "%1")
```
:::

::: { #func.msg.glue.args .sidebar }
##### Arguments
\

::: { #func.msg.glue.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

::: { #func.msg.glue.args.arg.name .sidebar }
  - **arg.name:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument. 
:::

::: { #func.msg.glue.args.arg .sidebar }
  - **arg:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.msg.glue.args.msg_template) argument.

::: { #func.msg.glue.details .sidebar }
##### Details
\

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.msg.glue.args.msg_template) and [arg](#func.msg.glue.args.arg)  arguments, respectively.

::: { #func.msg.glue.value .sidebar }
##### Value
\

::: { #func.msg.glue.code .sidebar }
##### Source Code
\

The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) function is shown below:
```{r eval=FALSE}
msg.glue <- function(msg_template, arg, arg.name = "%1"){
  msg_template |>
    msg.set_arg(arg, arg.name) |>
    str_glue()
}
```

::: {.noteblock data-latex=""}
The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) function is defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) script on _GitHub_.
:::
:::
